Clustering: A pipeline to analyse time-course gene expression data

### 2019-04-30 scripts/03_clustering.Rmd
FIX in scoring function

# Whether to filter genes
filter_genes = TRUE
keep_all_significant = FALSE
n_genes_to_keep = 5000
n_clusters = 20
percentage_genes_to_label = 0.5
```

@@

# Rescale the centroids
centroids = moanin:::rescale_values(kmeans_clusters$centroids)

all_scores = data.frame(row.names=row.names(data))
for(k in 1:n_clusters){
     scores = moanin:::score_genes_centroid(data, centroids[k,])
     all_scores[paste0("cluster_", k)] = scores
}

# Only assign labels to X% of the genes
max_score = quantile(moanin:::row_min(all_scores), c(percentage_genes_to_label))
genes_to_not_consider = moanin:::row_min(all_scores) >= max_score
labels = moanin:::row_argmin(all_scores)
labels[genes_to_not_consider] = NA
names(labels) = row.names(data)
```

@@

```{r fig.height=8, fig.width=8}
moanin:::plot_centroids(centroids, splines_model,
			colors=ann_colors$Group,
			smooth=TRUE)
```

>>>>

# Whether to filter genes
filter_genes = TRUE
keep_all_significant = FALSE
n_genes_to_keep = 10000
n_clusters = 20
percentage_genes_to_label = 0.5
```

@@

all_scores = matrix(NA, nrow=dim(data)[1], ncol=n_clusters)

for(k in 1:n_clusters){
     scores = moanin:::score_genes_centroid(
	data,
	kmeans_clusters$centroids[k,])
     all_scores[, k] = scores
}

# Only assign labels to X% of the genes
max_score = quantile(rowMin(all_scores), c(percentage_genes_to_label))
genes_to_not_consider = rowMin(all_scores) >= max_score
labels = apply(all_scores, 1, which.min)
labels[genes_to_not_consider] = NA
names(labels) = row.names(data)
```

```{r fig.height=8, fig.width=8}
par(mfrow=c(4, 5), mar=c(0.1, 0.1, 0.1, 0.1))
for(k in 1:n_clusters){
    hist(all_scores[k, ], breaks=20, col="black")
    abline(v=max_score, col="#AB0000")
}
```

@@

```{r fig.height=8, fig.width=8}
moanin:::plot_centroids(kmeans_clusters$centroids, splines_model,
			colors=ann_colors$Group,
			smooth=TRUE)
```
